SPARQL on the Open, Decentralised Web

### 2016-07-27 dissertation/conclusions.tex
Link to more in structure
Move etag labelling to future work

\section[Future Work]{Future work; Discussion of Other Problems}

@@

Problem~\ref{prob:queryeq} is best addressed by creating hashing
algorithms that have a reasonable chance of returning the same digest
if two queries are equivalent. As noted in Section~\ref{sec:relcache},
\cite{kaseicache} can be used for this, and the approach
\cite{papailiou2015graph} took to canonical labelling may be extended
to address this problem

>>>>

\section[Future Work]{Future work; Discussion of Other Problems}\label{sec:future}

@@

Problem~\ref{prob:queryeq} is has an interesting possible solution in
the application of hashing algorithms that have a reasonable chance of
returning the same digest if two queries are equivalent. As noted in
Section~\ref{sec:relcache}, \cite{kaseicache} can be used for this. It
is also interesting to discuss the approach \cite{papailiou2015graph}
took to canonical labelling in HTTP context:

The \httph{ETag} header, discussed in Section~\ref{sec:httpcache}, can
be used for a SPARQL result. Such a canonical label could be used in
conjunction with an algorithm that tracks changes to the RDF graph to
produce an \httph{ETag}. For slow-changing Linked Data, which is a
common case, it is a possibility that a canonical label in combination
with a time-stamp of the entire RDF Graph could yield considerable
benefits. However, the presented algorithm does not cover SPARQL in
its entirety, for example, it does not handle named graphs, solution
modifiers and filters, nor is it clear how it handles property paths
(which in many cases should be trivial, since a property path often
has an equivalent Basic Graph Pattern). Union queries or negation is
also not mentioned, so more work is needed for this method to have
general applicability. Nevertheless, if the entire Group Graph Pattern
of a certain query is supported, and the query projects all variables,
e.g. it wraps the pattern with \sparql{SELECT *} or
\sparql{CONSTRUCT}, the \httph{ETag} would be trivial to construct
using the presented algorithm in a non-trivial number of beneficial
cases. With this, cached result verification could be done by a
mediator using HTTP requests with the \httph{If-None-Match} header and
so make it possible to use parts of the engine of this paper usable in
the Internet infrastructure.

### 2016-07-27 dissertation/related.tex
Mention connected subgraphs in the problems instead
Move etag labelling to future work

The query planner first examines all connected subgraphs of a full
SPARQL query, and generates canonical labels for each one. Since it
insists on caching connected subgraphs, it avoids the problem I
encountered in Chapter~\ref{sec:tpfcacheplanning} that the cache may
break up connected subgraphs and thus create Cartesian joins. To
further enhance the query planner, the cache can optionally include
indexing. The authors also introduce the concept of
\textit{profitable} query patterns. It is not quite clear from the
text, but it seems this implies that the cache can also prefetch
results into the cache, if it finds that the result may benefit
subsequent queries.

The canonical labelling algorithm presented in this paper provides an
opportunity for further work, when considered in an HTTP context: The
\httph{ETag} header, discussed in Section~\ref{sec:httpcache}, can be
used for a SPARQL result. Such a canonical label could be
used in conjunction with an algorithm that tracks changes to the RDF
graph to produce an \httph{ETag}. For slow-changing Linked Data, which
is a common case, it is a possibility that a canonical label in
combination with a time-stamp of the entire RDF Graph could yield
considerable benefits. However, the presented algorithm does not cover
SPARQL in its entirety, for example, it does not handle named graphs,
solution modifiers and filters, nor is it clear how it handles
property paths (which in many cases should be trivial, since a
property path often has an equivalent Basic Graph Pattern). Union
queries or negation is also not mentioned, so more work is needed for
this method to have general applicability. Nevertheless, if the entire
Group Graph Pattern of a certain query is supported, and the query
projects all variables, e.g. it wraps the pattern with \sparql{SELECT
  *} or \sparql{CONSTRUCT}, the \httph{ETag} would be trivial to
construct using the presented algorithm in a non-trivial number of
beneficial cases. With this, cached result verification could be done
by a mediator using HTTP requests with the \httph{If-None-Match}
header and so make it possible to use parts of the engine of this
paper usable in the Internet infrastructure.

>>>>

The query planner first examines all connected subgraphs of a full
SPARQL query, and generates canonical labels for each one. To
further enhance the query planner, the cache can optionally include
indexing. The authors also introduce the concept of
\textit{profitable} query patterns. It is not quite clear from the
text, but it seems this implies that the cache can also prefetch
results into the cache, if it finds that the result may benefit
subsequent queries.
